Formalizing the Kolmogorov extension Theorem in Lean

### 2023-09-16 Manuscript/proof_outline.tex
remove blue

\noindent
Any ring is a semi-ring since $A\cap B = A \setminus (A \setminus B)$,
i.e.\ every ring is a $\pi$-system.
Using \leanline{variable {α : Type _} {s t : Set α}}, we define a semi-ring as follows:

@@

\noindent
\sloppy The second result states that for an outer measure induced by
an additive content on a semi-ring, we have $\sigma(\mathcal H)
\subseteq \mathcal F$. In particular, we then have defined a measure
on $\sigma(\mathcal H)$. This result is not yet covered in {\tt
  mathlib}. However, for product spaces, in
\leanline{MeasureTheory.Constructions.Pi}, there is
\leanline{pi_caratheodory}, which shows that $\sigma(\mathcal H)
\subseteq \mathcal F$ in {\color{blue} the construction of a product
  measure for a finite index set}. In addition, there is
\leanline{pi_pi_aux}, which shows that $\mu$ extends $m$ on $\mathcal
H$ in the same special case. See also \cite[Theorem
  2.5]{Kallenberg2020}.

>>>>

\noindent
Any ring is a semi-ring since $A\cap B = A \setminus (A \setminus B)$,
i.e.\ every ring is a $\pi$-system.
We define a semi-ring on a type \leanline{α} as follows:

@@

\noindent
\sloppy The second result states that for an outer measure induced by
an additive content on a semi-ring, we have $\sigma(\mathcal H)
\subseteq \mathcal F$. In particular, we then have defined a measure
on $\sigma(\mathcal H)$. This result is not yet covered in {\tt
  mathlib}. However, for product spaces, in
\leanline{MeasureTheory.Constructions.Pi}, there is
\leanline{pi_caratheodory}, which shows that $\sigma(\mathcal H)
\subseteq \mathcal F$ in the construction of a product
  measure for a finite index set. In addition, there is
\leanline{pi_pi_aux}, which shows that $\mu$ extends $m$ on $\mathcal
H$ in the same special case. See also \cite[Theorem
  2.5]{Kallenberg2020}.
